Insert the article title here

### 2020-07-25 tex/results.tex
try to declutter Rockstuhl section

We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
and $b=328$ nmn, since these dimension comply with the requirements of the quasistatic approximation.
They present the normalized scattering cross section of a SiC rectangular cylinder, and they perform simulation 
for two different setups. In Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
side of the geometry, which means that the electric field is parallel to the short side of the rectangle. Following, 
a similar analysis Rockstuhl Figure 14 (right) they have the wave vector (illumination) along the short
side of the geometry, which means that the electric field is parallel to the long side of the rectangle. These orientations,
correspond to the images (A) and (B) in the sketch presented in Figure \ref{fig:rectangle_sketch}.

Based on the results of the grid independence stud we decided to we used the density of the cube as a reference to 
produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
dimension we needed to chose a value that represents "infinity". To achieve this, we perform a study on the effects of 
elongate the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different values of the 
third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). 
We see that as we extend the third dimension the intensity of some peaks decreases, this is because some
of the peaks are related to the third dimension. Therefore, from now on we use $y=y=2688$ nm. It is worth 
noting that we could have increased this value more, however, the simulations will become computational
more expensive and we will still have the effects of having a 3D model.

@@

To generate the meshes for these simulations, we used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to produce regular triangles with the functions 
available. To overcome this, we created our own mesh using python scripts, and therefore 
obtain uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
on rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
as a factor that will introduce extra peaks on the response. We were not able to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results on the effect of uniformity and roundness. You can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results on Rockstuhl's work.

>>>>

We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
and $b=328$ nm, since these dimension comply well with the requirements of the quasistatic approximation needed 
to use \pygbe. In Rcokstuhl et al. work they present the normalized scattering cross section of a SiC rectangular 
cylinder, and they perform simulation for two different setups (see Figure \ref{fig:rectangle_sketch}). In 
Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
side of the geometry, which means that the electric field is parallel to the short side of the rectangle (like in 
Figure \ref{fig:rectangle_sketch} (B)). Following, a similar analysis Rockstuhl Figure 14 (right) they have the wave 
vector (illumination) along the short side of the geometry, which means that the electric field is parallel to the 
long side of the rectangle (like in Figure \ref{fig:rectangle_sketch} (A).

Based on the results of the grid independence study we decided to use the densities in the order of $6-9e^-5$
to produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
dimension we needed to chose a value that represents "infinity". To achieve this, we study the effects of 
elongation on the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different
values of the third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). We see that as we extend $y$ the 
intensity of some peaks decreases, this is because some of the peaks are related to this component. Therefore, 
from now on we use $y=2688$ nm. It is worth noting that we could have increased this value more, however, the
simulations will become computational more expensive and we will still have the effects of having a 3D model.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to produce regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using python scripts,
and create uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
as a factor that introduces extra peaks on the response. We were not able to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results on the effect of uniformity and roundness. You can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results on Rockstuhl's work.
